R Notebook

### 2020-01-23 src/testing_file.Rmd
avg ascii layer complete. mcp reprojected

>>>>

# mcp shape needs to be in wgs...

```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis - in aea
wgsraster <- raster("../output/maxent/predictions/com-split/apr/cloglog_1998_04_0.50576.asc") #just chosen randomly to act as dummy file
crs(wgsraster) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "
outsidemcp <- spTransform(outsidemcp, crs(wgsraster))
